Conversations in time: interactive visualisation to explore structured temporal data

### 2020-09-05 tsibbletalk.Rmd
figure 3 descriptions

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold',
  cache = TRUE, cache.path = 'cache/',
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
opts_knit$set(root.dir = here::here())
read_chunk("scripts/demo.R")
read_chunk("scripts/tourism.R")
```

@@

The shared tsibble data leverages the `key` attribute to converse with many coordinated views, with or without \CRANpkg{shiny}. On the other hand, a second critical attribute--`index`--lays the foundational temporal context that augments the conversation. When temporal data are plotted and stretched against the entire span like Figure \ref{fig:highlight-retail-1}, it puts the emphasis on the trend. When the data are wrapped over origin-less time units, such as one or two quarters, it makes seasonal patterns more pronounced. The \CRANpkg{tsibbletalk} package provides a shiny module

@@

@@

The {tsibbletalk} package provides a pair of UI and server functions, as a shiny module, to help with finding interesting time slices in a shiny application. The pair, decoupled to `tsibbleDiceUI()` and `tsibbleDiceServer()`, presents a clean interface and forms a resusable piece. Like all shiny modules, users should supply a unique session id. The UI function `tsibbleDiceUI()` shows a slider that controls the number of periods, and a plot specified by users. The server function `tsibbleDiceServer()` is the workhorse, transforming data and updating the plot. It expects a `ggplot` (converted to `plotly` via `ggplotly()`) or `plotly` object. This plot can be line charts, or other graphical elements (such as boxplots). But it assumes that tsibble's time index is plotted on the x-axis. The other mandatory argument is to specify the number of seasonal periods that requires shifting.

>>>>

```{r setup, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = 'figure/', fig.align = 'center', fig.show = 'hold',
  cache = TRUE, cache.path = 'cache/',
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
opts_knit$set(root.dir = here::here())
read_chunk("scripts/demo.R")
read_chunk("scripts/tourism.R")
read_chunk("scripts/pedestrian.R")
```

@@

The shared tsibble data leverages the `key` attribute to converse with many coordinated views, with or without \CRANpkg{shiny}. On the other hand, a second critical attribute--`index`--lays the foundational temporal context that augments the conversation. When temporal data are plotted and stretched against the entire span like Figure \ref{fig:highlight-retail-1}, it puts emphasis on the trend perception. Yet to digest periodic/aperiodic patterns, data should be wrapped over relative time units that are origin-less, such as one quarter or one day.

@@

The city of Melbourne has sensors installed to count hourly tallies of pedestrians in order to capture downtown daily rhythms (cite). Figure \ref{fig:wrap-ped} shows the first five months of 2020 foot traffic at four locations, with the depiction of three pronounced slices in time. Figure \ref{fig:wrap-ped-1} unfolds all counts from January to May on their absolute time scales, facetted by four sensors. On March 16, Melbourne went to the stage three lockdown due to COVID-19, seeing a significant decline in traffic volume across the city. These lines are then folded into daily and weekly sections, shown as Figure \ref{fig:wrap-ped-2} and \ref{fig:wrap-ped-3} respectively. Seasonal variations have been popped out to viewers, complementing the not-just-magnitude-drop data story. The pre-lockdown period is coloured with dark green and lockdown with orange.

Figure \ref{fig:wrap-ped} suggests that there could be more than one interesting time slices. The \CRANpkg{tsibbletalk} package provides a pair of UI and server functions, as a shiny module, to help with finding interesting seasonal slices in a shiny application. The pair, decoupled to `tsibbleDiceUI()` and `tsibbleDiceServer()`, presents a clean interface and forms a resusable piece. Like all shiny modules, users should supply a unique session id. The UI function `tsibbleDiceUI()` shows a slider that controls the number of periods, and a plot specified by users. The server function `tsibbleDiceServer()` is the workhorse, transforming data and updating the plot. It expects a `ggplot` (converted to `plotly` via `ggplotly()`) or `plotly` object. This plot can be line charts, or other graphical elements (such as boxplots). But it assumes that tsibble's time index is plotted on the x-axis. The other mandatory argument is to specify the number of seasonal periods that requires shifting.

```{r load-ped, eval = FALSE}
```

```{r ped-slice, echo = TRUE, eval = FALSE}
```

@@

### 2020-09-05 tsibbletalk.tex
figure 3 descriptions

The shared tsibble data leverages the \texttt{key} attribute to converse
with many coordinated views, with or without \CRANpkg{shiny}. On the
other hand, a second critical attribute--\texttt{index}--lays the
foundational temporal context that augments the conversation. When
temporal data are plotted and stretched against the entire span like
Figure \ref{fig:highlight-retail-1}, it puts the emphasis on the trend.
When the data are wrapped over origin-less time units, such as one or
two quarters, it makes seasonal patterns more pronounced. The
\CRANpkg{tsibbletalk} package provides a shiny module

@@

@@

The \{tsibbletalk\} package provides a pair of UI and server functions,
as a shiny module, to help with finding interesting time slices in a
shiny application. The pair, decoupled to \texttt{tsibbleDiceUI()} and
\texttt{tsibbleDiceServer()}, presents a clean interface and forms a
resusable piece. Like all shiny modules, users should supply a unique
session id. The UI function \texttt{tsibbleDiceUI()} shows a slider that
controls the number of periods, and a plot specified by users. The
server function \texttt{tsibbleDiceServer()} is the workhorse,
transforming data and updating the plot. It expects a \texttt{ggplot}
(converted to \texttt{plotly} via \texttt{ggplotly()}) or
\texttt{plotly} object. This plot can be line charts, or other graphical
elements (such as boxplots). But it assumes that tsibble's time index is
plotted on the x-axis. The other mandatory argument is to specify the
number of seasonal periods that requires shifting.

>>>>

The shared tsibble data leverages the \texttt{key} attribute to converse
with many coordinated views, with or without \CRANpkg{shiny}. On the
other hand, a second critical attribute--\texttt{index}--lays the
foundational temporal context that augments the conversation. When
temporal data are plotted and stretched against the entire span like
Figure \ref{fig:highlight-retail-1}, it puts emphasis on the trend
perception. Yet to digest periodic/aperiodic patterns, data should be
wrapped over relative time units that are origin-less, such as one
quarter or one day.

@@

The city of Melbourne has sensors installed to count hourly tallies of
pedestrians in order to capture downtown daily rhythms (cite). Figure
\ref{fig:wrap-ped} shows the first five months of 2020 foot traffic at
four locations, with the depiction of three pronounced slices in time.
Figure \ref{fig:wrap-ped-1} unfolds all counts from January to May on
their absolute time scales, facetted by four sensors. On March 16,
Melbourne went to the stage three lockdown due to COVID-19, seeing a
significant decline in traffic volume across the city. These lines are
then folded into daily and weekly sections, shown as Figure
\ref{fig:wrap-ped-2} and \ref{fig:wrap-ped-3} respectively. Seasonal
variations have been popped out to viewers, complementing the
not-just-magnitude-drop data story. The pre-lockdown period is coloured
with dark green and lockdown with orange.

Figure \ref{fig:wrap-ped} suggests that there could be more than one
interesting time slices. The \CRANpkg{tsibbletalk} package provides a
pair of UI and server functions, as a shiny module, to help with finding
interesting seasonal slices in a shiny application. The pair, decoupled
to \texttt{tsibbleDiceUI()} and \texttt{tsibbleDiceServer()}, presents a
clean interface and forms a resusable piece. Like all shiny modules,
users should supply a unique session id. The UI function
\texttt{tsibbleDiceUI()} shows a slider that controls the number of
periods, and a plot specified by users. The server function
\texttt{tsibbleDiceServer()} is the workhorse, transforming data and
updating the plot. It expects a \texttt{ggplot} (converted to
\texttt{plotly} via \texttt{ggplotly()}) or \texttt{plotly} object. This
plot can be line charts, or other graphical elements (such as boxplots).
But it assumes that tsibble's time index is plotted on the x-axis. The
other mandatory argument is to specify the number of seasonal periods
that requires shifting.

\begin{Schunk}
\begin{Sinput}
p_line <- pedestrian20 %>%
  ggplot(aes(x = Date_Time, y = Count, colour = Lockdown)) +
  geom_line(size = .3) +
  facet_wrap(~ Sensor, scales = "free_y") +
  labs(x = "Date Time") +
  scale_colour_brewer(palette = "Dark2") +
  theme(legend.position = "none")

ui <- fluidPage(tsibbleDiceUI("dice"))
server <- function(input, output, session) {
  tsibbleDiceServer("dice", ggplotly(p_line, height = 700), period = "1 day")
}
shinyApp(ui, server)
\end{Sinput}
\end{Schunk}

@@
